Using Andersen’s model of health care utilization to assess factors associated with COVID-19 testing among adults in Bangladesh: an online survey

### 2021-11-11 code/analysis_code/analysisscript.Rmd
table

```{r}
library(tidymodels)
library(readr)       # for importing data
library(tidyverse)
library(dotwhisker)
library(broom.mixed)
library(here)
```

@@

#load data. 
```{r}
mydata <- readRDS(data_location)
glimpse(mydata)
```

>>>>

```{r}
library(tidymodels)
library(readr)       # for importing data
library(tidyverse)
library(dotwhisker)
library(broom.mixed)
library(table1)
library(here)
```

@@

#load data. 
```{r}
mydata <- readRDS(data_location)
View(mydata)
```

#get a table
```{r}
overall_summary <- table1(~ Age + Sex + education + economic_status + student_or_heathworker + residence + trusted_source + work_from_home + quarantined_or_not + infection_status_info + worry_level + chronic_disease_history + social_distance_practice + follow_preventive_measure   , data=mydata, overall="Total")
overall_summary
```
```{r}
df100 = data.frame(overall_summary)
summarytable_file = here("results", "Overall.rds")
saveRDS(df100, file = summarytable_file)
```

### 2021-11-11 code/processing_code/processingscript.Rmd
table

```{r}
processeddata1 <- rawdata %>% rename ("education" = `Highest educational level`,
                               "student/heathworker" = `Are you a student or worker in the healthcare sector?`,
                               "economic_status" = 'Which of the following categories best describes your current socio-economic situation?',
                               "residence" = `Do you live in:`,
                               "trusted_source" = `Which source of COVID-19 information/advice do you trust the most?`,
                               "work_from_home" = 'Are you currently working/studying from home because of the COVID-19 outbreak?',
                               "quarantined_or_not" = `Have you been quarantined (either at home or else where) at any point in time during the Covid-19 epidemic?`,
                               "infection_status_info" = `Since the beginning of the COVID-19 outbreak, do you have information on your infection status?`,
                               "worry_level" = `How worried/fearful are you about becoming (re)infected by the coronavirus?: On a scale of 1 to 5`,)
```

>>>>

```{r}
processeddata1 <- rawdata %>% rename ("education" = `Highest educational level`,
                               "student_or_heathworker" = `Are you a student or worker in the healthcare sector?`,
                               "economic_status" = `Which of the following categories best describes your current socio-economic situation?`,
                               "residence" = `Do you live in:`,
                               "trusted_source" = `Which source of COVID-19 information/advice do you trust the most?`,
                               "work_from_home" = `Are you currently working/studying from home because of the COVID-19 outbreak?`,
                               "quarantined_or_not" = `Have you been quarantined (either at home or else where) at any point in time during the Covid-19 epidemic?`,
                               "infection_status_info" = `Since the beginning of the COVID-19 outbreak, do you have information on your infection status?`,
                               "worry_level" = `How worried/fearful are you about becoming (re)infected by the coronavirus?: On a scale of 1 to 5`,
                               "chronic_disease_history" = `Do you have any of the following chronic/underlying diseases? (many answers possible): None of the above`,
                              "social_distance_practice" = `During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): Social distancing of at least 1.5m`,
                              "follow_preventive_measure" = `During the past 7 days, have you been observing any of the following preventive measures against COVID-19? (Tick all answers that apply): None of the above`)
```

### 2021-11-11 products/manuscript/Manuscript.Rmd
table

@@

Among the participants, **78.9%** are less than or equal  to 35 years old. That indicates that majority of the participants tend to be younger. While **45.18%** of the participants were female, **54.82%** were male, which shows less chance of biad due to sex. **78.05%** of the participants had a bachelor or post-bachelor degree, clearly indicating that majority of the participants had pretty good education background. Almost **50%** of the participants belongs to "upper middle income category", indicating that at least half of the participants don't belong to the poorer side. Less than **10%** of the participants live in a village/rural area. Health professionals and Tv/radio seems to be the most trusted source to the participants. Apparently equal half of the participants worked from home or not at some stage of the study. Major half of the participants did quarantine at some stage during the study. **63%** of the participants didn't go through a COVID test. Almost half of the participants **(46%)** were moderate or more worried about reinfection. Only **22%** of the participants recorded to have some sort of chronic disease. **(This data can be accessed/viewd through the "supplementary.rmd" file)**

>>>>

```{r summarytable,  echo=FALSE}
resulttable=readRDS("../../results/Overall.rds")
knitr::kable(resulttable, caption = "**Overall Descriptive Statistics of the Participants**")
```

@@

Among the participants, **78.9%** are less than or equal  to 35 years old. That indicates that majority of the participants tend to be younger. While **45.18%** of the participants were female, **54.82%** were male, which shows less chance of biad due to sex. **78.05%** of the participants had a bachelor or post-bachelor degree, clearly indicating that majority of the participants had pretty good education background. Almost **50%** of the participants belongs to "upper middle income category", indicating that at least half of the participants don't belong to the poorer side. Less than **10%** of the participants live in a village/rural area. Health professionals and Tv/radio seems to be the most trusted source to the participants. Apparently equal half of the participants worked from home or not at some stage of the study. Major half of the participants did quarantine at some stage during the study. **63%** of the participants didn't go through a COVID test. Almost half of the participants **(46%)** were moderate or more worried about reinfection. Only **22%** of the participants recorded to have some sort of chronic disease. **(Separate analysis for each variable was done and the data can be accessed/viewd through the "supplementary.rmd" file)**
